Calculating life expectancy and exploring missingness

### 2016-10-26 Code/1_Explore_Data_v2.Rmd

    ct.black <- subset(dat.clean, StateYearRaceSex == paired.ids[i, "StateYearRaceSexBlack"]) %>% 
                ungroup() %>%
                select(Age2, COD2, cod_prop_death5) %>%
                rename(prop.black = cod_prop_death5)
    ct.both <- merge(ct.white, ct.black, by = c("Age2", "COD2"))

test1 <- cause_of_death_decomp(life.table1 = as.data.frame(list.life.tables[[black.index]]), 
                                                 life.table2 = as.data.frame(list.life.tables[[white.index]]), 
                                                 decomp.table = as.data.frame(list.age.decomp.tables[[i]]),
                                                 cod.table = ct.both, "Age2", "COD2", "prop1", "prop2")

@@

age_contr1 <- test1 %>% ungroup() %>% group_by(Ages) %>% summarise(age_contribution = sum(C_xi))
sum(age_contr1$age_contribution)
age_contr2 <- test2 %>% ungroup() %>% group_by(Ages) %>% summarise(age_contribution = sum(C_xi))
sum(age_contr2$age_contribution)
```

>>>>

    ct.black <- subset(dat.clean, StateYearRaceSex == paired.ids[i, "StateYearRaceSexBlack"]) %>% 
                ungroup() %>%
                select(Age2, COD2, cod_prop_death5) %>%
                rename(prop.black = cod_prop_death5)
    ct.both <- merge(ct.white, ct.black, by = c("Age2", "COD2")) 
    ct.both <- ct.both %>% arrange(COD2)

test1 <- cause_of_death_decomp(life.table1 = as.data.frame(list.life.tables[[black.index]]),
                               life.table2 = as.data.frame(list.life.tables[[white.index]]), 
                               decomp.table = as.data.frame(list.age.decomp.tables[[i]]),
                               cod.table = ct.both, 
                               age.colname.cod.table = "Age2", 
                               COD.colname.cod.table = "COD2", 
                               prop1.colname.cod.table = "prop.black", 
                               prop2.colname.cod.table = "prop.white")

@@

age_contr1 <- test1 %>% ungroup() %>% group_by(Ages) %>% summarise(age_contribution = sum(C_xi))
age_contr1
list.age.decomp.tables[[i]]
#compare -- see that there is something wrong with the age labels in one or the other... 
#all the same numbers but some of them are in a strange order.

age_contr2 <- test2 %>% ungroup() %>% group_by(Ages) %>% summarise(age_contribution = sum(C_xi))
sum(age_contr2$age_contribution)
```
